\section{Product perspective}
The system that will eventually be released is composed of four major components:
\begin{itemize}
\item A mobile application for passengers;
\item A web application for passengers;
\item A mobile application for taxi driver;
\item The backend infrastructure to manage the service.
\end{itemize}
In particular, we expect the new system to fully replace any mechanism that the city administration had previously in place for the management of taxi calls.


\subsection{System interfaces}
The system has to be designed to be expandable, in order to let other developers implement new functionalities in the future should they be needed. This implies that the system will have to provide a proper set of APIs to expose its core functionalities to external plugins. 


\subsection{User interfaces}
The mobile application should natively support both smartphones and tablets by offering a uniquely optimized user interface tailored to the specific kind of device being used. 

Furthermore, the mobile application should be resolution independent; in particular, it should support all display sizes comprised between 3” and 6” (when used on a mobile phone) and between 7” and 12” (when used on a tablet).

The web application should properly address dynamic web page resizing by proportionally scaling header, footer and side bars to the amount of available space without stretching individual components and forms. It should also be offered both in a desktop version and in a mobile-friendly version.

In addition, both the mobile application and the web application should be designed to be accessible by blind people, that means that it should be possible for a screen reader software to correctly interpret them in a meaningful way.


\subsection{Hardware interfaces}
The system should support smartphones and tablets as end-user terminals by offering mobile applications both for taxi drivers and passengers.

In order to maximize the accessibility of the service, the system should offer a native application for the three major mobile platforms (iOS, Android, Windows Phone).

The central system should be designed to run on standard x86 server machines.


\subsection{Software interfaces}
The system will have to communicate with an external mapping service in order to use the functionalities of GPS location decoding (note: must be specified what we mean) and waiting time estimation.

The system will also interface with a commercial DBMS in order to store and retrieve data and perform queries over it.


\section{Product functions}


\section{User characteristics}
Stakeholders: (non va qui però!!!)
Users: men/women that want to require a taxi and that will use the system to accomplish this.

Taxi drivers: the men/women that drive the taxi; they are supposes to answers to users' request (by means of the system) and drive them to the desired location.

City government: it is the main stakolder of the project, since it is the one who committed it and that will pay for it.

Mobile phone producer: the company with whom the city government needs to manage an agreement  to provide mobile phone to all the taxi drivers.

Taxi drivers’ union: as the system will have an impact on the way taxi drivers work, it's necessary to consider some possibile hostile action from their unions.

training and user support staff???

\section{Constraints}

\section{Assumptions and dependencies}
\subsection{Domain properties}
\begin{itemize}
\item Zones do not overlap.
\item User can only request rides using either the web application or the mobile application provided by the system.
- [OR] Users do not request rides using their personal acquaintance with taxi drivers.
\item Taxi drivers will only make rides by accepting a request from the system.
\item Contact information of taxi drivers are not disclosed by the city administration.
\item All the data already stored in the system-as-is is actually transferred to the system-to-be when it is put into operation. [related req.: how can we transfer this data?]
\item Uses don't have the need to choose a particular taxi driver among those that are available for their ride.
\item Users do not have to confirm the choice of the selected taxi.
\item The city council has divided the city in taxi zones.
\item The taxi service is operated 24h/day, unless exceptional circumstances occur. ***
\item In case any exceptional circumstance occur for which the taxi service cannot be operated, the system is not required to satisfy incoming and reserved requests. 
\item For any given GPS location inside the boundaries of the city, it is always possible to reverse-decode it into a valid city address. 
\item A taxi driver will take a passenger onboard if and only if both the taxi code and the security number sent to the passenger are equal to his own. 

*** exceptional circumstance: strikes, severe weather conditions, service suspension decided by the city council, particular holidays… [terminology]
\item Every taxi driver is provided with a business mobile phone by the city council.
\item The business phone of every taxi driver has always an active data plan.
\item Every taxi is uniquely identified by an alphanumeric code that is assigned by the city administration when he becomes part of the taxi service.
\end{itemize}

\subsection{Assumptions}
\begin{itemize}
\item Users are not allowed to place reservations more than 15 days in advance. 
\item The city council may decide to update the taxi zone division in the future. 
\item The only taxis eligible for fulfilling a reservation are the ones that are present in the queue of the zone associated with the reservation source address 10 minutes before the scheduled meeting time.
\item In order to receive ride requests, a taxi driver must explicitly mark himself as available.
\item A taxi driver will not be able to receive ride requests while he’s unavailable.
\item Taxis that are considered to be out-of-city will not be able to receive calls. (redundant?)
\item A taxi driver who is currently on a ride will not be able to receive calls.
\item A taxi driver must always notify the system when he terminates a ride. 
\item A user is not required to be registered in order to request a ride.
\item A user must be registered and logged in to the system in order to reserve a ride.
\item After a taxi driver has been associated to a call, he must confirm or refuse the request within two minutes. After that period of time, the call is considered refused. 
\end{itemize}

- Traffic information and route data can be obtained from a third party mapping service.

- A user that has already requested a taxi will not request another one before having completed his ride.