\chapter{Introduction}
\section{Revision History}
\begin{center}
\begin{longtable}{|l|l|l|l|}
\hline
Version &
Date &
Author(s) &
Summary \\
\hline
1.0 &
21/01/16 &
Valerio Castelli \& Fabrizio Casati &
Initial release \\
\hline
\end{longtable}
\end{center}

\section{Purpose and Scope}
This document represents the Integration Testing Plan Document for myTaxiService. 
Integration testing is a key activity to guarantee that all the different subsystems composing myTaxiService interoperate consistently with the requirements they are supposed to fulfill and without exhibiting unexpected behaviors. 
The purpose of this document is to outline, in a clear and comprehensive way, the main aspects concerning the organization of the integration testing activity for all the components that make up the system.
In the following sections we're going to provide:
\begin{itemize}
	\item A list of the subsystems and their subcomponents involved in the integration activity that will have to be tested
	\item The criteria that must be met by the project status before integration testing of the outlined elements may begin 
	\item A description of the integration testing approach and the rationale behind it
	\item The sequence in which components and subsystems will be integrated 
	\item A description of the planned testing activities for each integration step, including their input data and the expected output 
	\item A list of all the tools that will have to be employed during the testing activities, together with a description of the operational environment in which the tests will be executed
\end{itemize}
\section{Definitions, Acronyms, Abbreviations}
\subsection{Definitions}
\begin{itemize}
	\item Subcomponent
	\item Subsystem\note{TBD}
\end{itemize}
\subsection{Acronyms}
\begin{itemize}
	\item SDD: Software Design Description.
	\item DD: Design Document. Used as a synonym of SDD.
	\item DBMS: Database Management System.
	\item API: Application Programming Interface.
	\item RASD: Requirement Analysis and Specification Document.
	\item SRS: Software Requirements Specifications. Synonym of RASD.
	\item ETA: Estimated Time of Arrival.
	\item UI: User Interface.
	\item GPS: Global Positioning System.
\end{itemize}
\subsection{Abbreviations}
\begin{itemize}
	\item Req. as for Requirement.
	\item WebApp as for Web Application.
\end{itemize}
\section{Reference Documents}
\begin{itemize}
	\item The project description document: Assignments 1 and 2 (RASD and DD).pdf
	\item Assignment document: Assignment 4 - integration test plan.pdf
	\item myTaxiService Requirement Analysis and Specification Document: RASD.pdf
	\item myTaxiService Design Document: DD.pdf
	\item The Integration Test Plan Example document: Integration Test Plan Example.pdf
\end{itemize} 