\chapter{Introduction}
\section{Revision History}
\begin{center}
\begin{longtable}{|l|l|l|l|}
\hline
Version &
Date &
Author(s) &
Summary \\
\hline
1.1 &
29/02/16 &
Valerio Castelli \& Fabrizio Casati &
Minor fixes \\\hline
1.0 &
26/01/16 &
Valerio Castelli \& Fabrizio Casati &
Initial release \\
\hline
\end{longtable}
\end{center}
\section{Purpose and scope}
This document represents the Project Plan Document for myTaxiService.

Its main purpose is to analyze the expected complexity of myTaxiService and assist the project leader in the delicate phase of cost and effort estimation. This information can be subsequently used as a guidance to define the required budget, the resources allocation and the schedule of the activities. 

In the first section, we're going to use the Function Points and COCOMO approaches together to provide an estimate of the expected size of myTaxiService in terms of lines of code and of the cost/effort required to actually develop it.

In the second section, we'll reuse these figures to propose a possible schedule for the project that covers all activities from the requirements identification to the implementation and testing activities. 

In the third section we're going to assign the different members of our development group to the various tasks.

Finally, we're going to elaborate on the possible risks that myTaxiService could face during the various phase of the project and provide some general conclusions.
\section{Definitions, Acronyms, Abbreviations}
\subsection{Definitions}
\subsection{Acronyms}
\begin{itemize}
	\item FP: Function Points.
	\item ILF: Internal logic file
	\item ELF: External logic file.
	\item EI: External Input.
	\item EO: External Output.
	\item EQ: External Inquiries.
	\item DBMS: Database Management System.
	\item API: Application Programming Interface.
	\item ETA: Estimated Time of Arrival.
	\item UI: User Interface.
	\item GPS: Global Positioning System.
\end{itemize}
\subsection{Abbreviations}
\section{Reference Documents}
\begin{itemize}
	\item Assignment document: Assignment 5 - Project Plan.pdf
	\item myTaxiService Requirement Analysis and Specification Document: RASD.pdf
	\item The Project Plan Example documents: Example of usage of FP and COCOMO for Assignment 5.pdf and Second example of usage of FP and COCOMO for Assignment 5.pdf
	\item The Function Points complexity evaluation tables.
	\item The COCOMO II Model Definition Manual (version 2.1,  1995 – 2000 Center for Software Engineering, USC).
\end{itemize} 